14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-11 rules/rules19.tex
Rules: Update system description information.

  \item {\it Mandatory System Descriptions.} \todo{}

@@

\header{System description.}
%
As part of a submission, SMT-COMP entrants \emph{must} provide a short (1--2
pages) description of the system.
This should include a list of all authors of the system, their present
institutional affiliations, and any appropriate acknowledgements.  The
programming language(s) and basic SMT solving approach employed should
be described (e.g., lazy integration of a Nelson-Oppen combination
with SAT, translation to SAT, etc.).  System descriptions should also
include a URL for a web site for the submitted tool.  System
descriptions may be submitted after the solver deadline, but to be
useful should be sent to the organizers before the competition ends.
We intend to make system descriptions publicly available.

@@

\header{Wrapper tools.}
%
A \emph{wrapper tool} is defined as any solver that calls (or is in
some other way based on) one or more SMT solvers not written by the
author of the wrapper tool.  The other solvers are called the
\emph{wrapped} solvers.  A wrapper tool must explicitly acknowledge
any solvers that it wraps.  Its system description should make clear
the technical innovations by which the wrapper tool expects to improve
on the wrapped solvers.

>>>>

  \item {\it Mandatory System Descriptions.}
    SMT-COMP entrants are now required to provide a short (1–2 pages)
    description of the system.  \emph{Rationale:} The main incentive for this
    change is twofold.  First, we want to improve transparency when submitted
    solvers are wrapper tools according to the rules of the competition.
    Second, we want to encourage documentation of technical improvements that
    lead to the current results.

@@

\header{System description.}
%
As part of the submission, SMT-COMP entrants are \emph{required} to provide a
short (1–-2 pages) description of the system.  This should include a list of
all authors of the system, their present institutional affiliations, and any
appropriate acknowledgements.  The programming language(s) and basic SMT
solving approach employed should be described (e.g., lazy integration of a
Nelson-Oppen combination with SAT, translation to SAT, etc.).  System
descriptions should also include a URL for a web site for the submitted tool.
System descriptions must be submitted until the final solver deadline System
descriptions will be made publicly available.

@@

\header{Wrapper tools.}
%
\todo{Giles: update}
A \emph{wrapper tool} is defined as any solver that calls (or is in
some other way based on) one or more SMT solvers not written by the
author of the wrapper tool.  The other solvers are called the
\emph{wrapped} solvers.  A wrapper tool must explicitly acknowledge
any solvers that it wraps.  Its system description should make clear
the technical innovations by which the wrapper tool expects to improve
on the wrapped solvers.
